### 2021-08-25 README.Rmd
Fix the check error and update documentation.
Correcting the df name in Readme.

-  `wages_hs2020`: The wages data from the cohort whose highest grade completed is up to 12th grade.
-  `wages_hs_dropout`: The wages data of the high school dropouts.
-  `demographic_nlsy79`: The demographic data of the NLSY79 cohort.

@@

Here is the example of plotting some samples of subjects in `wages_hs2020` using `brolgar` (Tierney, Cook, and Prvan, 2020).

```{r}
library(yowie)
library(brolgar)
library(ggplot2)

>>>>

-  `wages_hs`: The wages data from the cohort whose highest grade completed is up to 12th grade.
-  `wages_hs_do`: The wages data of the high school dropouts.
-  `demog_nlsy79`: The demographic data of the NLSY79 cohort.

@@

Here is the example of plotting some samples of subjects in `wages_hs` using `brolgar` (Tierney, Cook, and Prvan, 2020).

```{r, message=FALSE}
library(yowie)
library(brolgar)
library(ggplot2)
